\section{Preliminary Plan}
Our plan essentially has two stages: data exploration and transfer learning. 
\subsection{Milestones}
\begin{enumerate}
    \item Project Scoping(Feb 25th): Provide a scope of work to be attempted and problem framing.
    \item Data Exploration and Clustering(March 15th): Application of Data Mining algorithms to visualize and explore clusters both of query terms and documents.
    \item Transfer Learning Labels(March 28): using finding from data exploration and clustering we will create processed data to be used with our transfer tasks.
    \item Synonym Evaluation dataset and Baselines(March 28th):Finalize query synonym prediction task and produce baselines that do not leverage click data.
    \item Query Rewriting baseline(March 28): Finalize query rewriting task and produce baselines that do not leverage click data.
    \item Midterm Report(March 30): discuss progress and learning.
    \item Experiments across tasks(April 15th): Initial results using transfer data on benchmark tasks. Use results to go back and tweak mining methods.
    \item Experiments across tasks v2(April 30): Updated results using improved data.
    \item Final report (May 5th)
\end{enumerate}
\subsection{Roles}
\begin{itemize}
  \item \textbf{Daniel Campos}: Application of Data Mining techniques to dataset for exploration and transfer label creation, report writing, IR experiments
  \item \textbf{Revanth Reddy}: Query rewriting baseline, experiments and tweaking.
  \item \textbf{Shweta Garg}: Synonym predicting baseline, experiments and tweaking. 
\end{itemize}
